WordRec Experiment

### 2018-12-28 Analysis/process.Rmd
new modif on manuscript

Processing for IRB

```{r}
d1 <- read_delim("data_real1.txt", delim = " ")  %>%
  filter(code != 'test',
         !is.na(code)) %>%
  distinct(ID, gender, age, code)

d2 <- read_delim("data_real2.txt", delim = " ") %>%
  filter(code != 'test',
         !is.na(code)) %>%
  distinct(ID, gender, age, code)

d3 <- read_delim("data_winter.txt", delim = " ") %>%
  filter(code != 'test',
         !is.na(code)) %>%
  distinct(ID, gender, age, code)

d_all <- d1 %>%
  bind_rows(d2) %>%
  bind_rows(d3) %>%
  rowwise() %>%
  mutate(date = strsplit(code, split = "-")[[1]][2]) %>%
  select(-code, -ID)

d_final <- cbind(subjects = rownames(d_all), d_all)  %>%
  mutate(ID= paste('child_', subjects, sep="")) %>%
  select(ID, gender, age, date)

write.csv(d_final, file = "data_IRB_fourtassi.csv")

@@

d_sim <- read_delim("sim_results.txt", delim = " ")  %>%
  filter(condition != "obj_prac" & condition != "sound_prac") %>%
  filter(problem == 'No')

d_sim_summary <- d_sim %>%
  group_by(condition, distance) %>%
  summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se)

d_sim_transform <-  d_sim_summary %>%
  mutate(scale1 = (mean-1)/6) %>%
  mutate(myscale =ifelse(condition=='sound_real', scale1/0.926, scale1))

@@

ggplot(d_sim_summary, 
      aes(x = distance, y = mean)) +
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                 position = position_dodge(width = .1)) + 
  xlab("Distance") +ylab("rating")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) + facet_grid(.~condition)

@@

#Maximal (does not converge)
model_ch <- glmer(iscorrect ~ s_dist * c_dist + 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | item_object) + 
                 (s_dist | item_sound), 
               data = data_ch, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

@@

#1) Simplify random structure till the model converges

#Drop interaction from random slope per subject (Stil does not converge)
model1 <- glmer(iscorrect ~ s_dist * c_dist + 
                 (s_dist + c_dist  | ID) + 
                 (1 + c_dist| item_object) + 
                 (1 + s_dist| item_sound), 
               data = data_model, family = binomial())

#Drop random slope per stimuli  (hooray! This one converges now)
model2 <- glmer(iscorrect ~ s_dist * c_dist + 
                 (s_dist + c_dist  | ID) + 
                 (1 | item_object) + 
                 (1 | item_sound), 
               data = data_model, family = binomial(),
              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

model00 <- mixed(iscorrect ~ s_dist * c_dist + 
                 (s_dist + c_dist  | ID) + 
                 (1 | item_object) + 
                 (1 | item_sound), 
                 method = "LRT",
               data = data_model, family = binomial(),
              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#2) Use likelihood ration to prune fixed effects

#drop interaction term from fixed effect (This works! less degrees of freedom and similar explanatory power)

model3 <- glmer(iscorrect ~ s_dist + c_dist + 
                 (s_dist + c_dist  | ID) + 
                 (1 | item_object) + 
                 (1 | item_sound), 
               data = data_model, family = binomial())

anova(model2, model5)

@@

```{r fig.width=2.5, fig.height=1.2}
hi <- get_speaker_statistics()

hello <- hi %>%
  #filter(speaker_role=="Target_Child") %>%
  mutate(age = round(target_child_age/12)) %>%
  filter(age <11) %>%
  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
  group_by(age, role, target_child_sex) %>%
  summarise(utt = sum(num_utterances)) %>%
  filter(target_child_sex == 'male' | target_child_sex == 'female') %>%
  rename(gender = target_child_sex) %>%
  mutate(gender2 = ifelse(gender=='male', 'male children', 'female children'))

ggplot(hello, 
      aes(x = age, y = utt, col = factor(role))) +
  geom_point()+
  geom_line(aes(lty=factor(role))) + 
  scale_x_continuous(breaks=c(1,2,3,4, 5, 6, 7,8,9, 10)) +
  #scale_y_continuous(name="number of utterances", labels = scales::comma) +
  scale_y_continuous(labels = scales::comma) +
  xlab("Age (years)") +ylab("Number of utterances")+
  guides(col=guide_legend(title="Speaker"), lty=guide_legend(title="Speaker"))+
  facet_grid(.~gender2)

  #geom_hline(yintercept = 0.50) +
  #xlab("Aud distance") +ylab("% Accurate")+
  #scale_colour_discrete(name="Vis Dist")+
#theme(legend.title = element_text(size=8))

hello <- hi %>%
  #filter(speaker_role=="Target_Child") %>%
  mutate(age = round(target_child_age/12)) %>%
  filter(age <11) %>%
  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
  group_by(age, role, ) %>%
  summarise(utt = sum(num_utterances)) #%>%
  #filter(target_child_sex == 'male' | target_child_sex == 'female')

Simualte the probability space

@@

Now I need to predict accuracy as function of sound and meaning similarity 
```{r}

#This the analytical solution of the posterior + luce rule
combine_cues <- function(s, o, Vr) {
  s1 = 0
  o1 = 0
  no_acc <- exp(-(s1-s)^2/(2*Vr)) + exp(-(o1-o)^2/(2*Vr))
  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*Vr)) 
  acc_norm <- acc/(acc+no_acc)

@@

combine_cues_2 <- function(s, o, Vr_s, Vr_o) {
  s1 = 0
  o1 = 0
  no_acc <- exp(-(s1-s)^2/(2*Vr_s)) + exp(-(o1-o)^2/(2*Vr_o))
  acc <- 1 + exp(-((s1-s)^2/(2*Vr_s)+(o1-o)^2/(2*Vr_o))) 
  acc_norm <- acc/(acc+no_acc)

@@

fit_adults <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.01), lower=c(0), algorithm="port")

fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.04, Vr_o=0.04), lower=c(0,0), algorithm="port")

@@

fit_children <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.3), lower=c(0), algorithm="port")

fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.3, Vr_o=0.3), lower=c(0,0), algorithm="port")

@@

@@

@@

s = seq(-1,1.5,0.01)
y = Gdist(0,1,x)

illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), x.pos = "0", type='within') %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='within')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='between')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between'))

ggplot(illustration, aes(x=x, y=y, col=x.pos)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      aspect.ratio = 0.7
      )+
  #xlim(c(-1,1))+
  #ylim(c(0,1))+
  #geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("position") + ylab("Prob") #+
  #facet_grid(.~object_distance)

>>>>

@@

d_sim <- read_delim("sim_results.txt", delim = " ")  %>%
  filter(condition != "obj_prac" & condition != "sound_prac") %>%
  filter(problem == 'No') %>%
  mutate(scaled = (answer-1)/6)

d_sim_summary <- d_sim %>%
  group_by(condition, distance) %>%
  summarise(mean = mean(scaled),
                   sd = sd(scaled),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se)

d_sim_transform <-  d_sim_summary %>%
  mutate(normalized =ifelse(condition=='sound_real', mean/0.926, mean)) %>% #Here I only normalize sounds, objects are already normalized
  filter(distance != "iden") %>%
  mutate(mydist = ifelse(distance=="0.6", 1, myscale))%>% # Here I create a ligne for different which were not explicitly asked from participants because it was used as a prototype, thus dist=1
  mutate(labels = ifelse(distance=='0.1','similar', 
                         ifelse(distance=='0.3','intermediate', 
                                ifelse(distance=='sim','similar',
                                       ifelse(distance=='med','intermediate', 'different')))))

@@

ggplot(d_sim_transform, 
      aes(x = labels, y = mydist, col=condition)) +
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
     #            position = position_dodge(width = .1)) + 
  xlab("Distance") +ylab("rating")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) +
  ylim(c(0,1.1))

@@

#Maximal random structure
model_ch <- glmer(iscorrect ~ s_dist * c_dist + 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | item_object) + 
                 (s_dist | item_sound), 
               data = data_ch, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

@@

@@

Use values of perceptual distance from the similarity judgement task

@@

Now I need to predict accuracy as a function of sound and meaning similarity 
```{r}

#This the analytical solution of the posterior + luce rule
combine_cues <- function(s, o, Vr) {
  s1 = 0
  o1 = 0
  no_acc <- exp(-(s1-s)^2/(2*(Vr)^2)) + exp(-(o1-o)^2/(2*(Vr)^2))
  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*(Vr)^2)) 
  acc_norm <- acc/(acc+no_acc)

@@

combine_cues_2 <- function(s, o, Vr_s, Vr_o) {
  s1 = 0
  o1 = 0
  no_acc <- exp(-(s1-s)^2/(2*(Vr_s)^2)) + exp(-(o1-o)^2/(2*(Vr_o)^2))
  acc <- 1 + exp(-((s1-s)^2/(2*(Vr_s)^2)+(o1-o)^2/(2*(Vr_o)^2))) 
  acc_norm <- acc/(acc+no_acc)

@@

fit_adults <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.1), lower=c(0), algorithm="port")

fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.04), lower=c(0,0), algorithm="port")

@@

fit_children <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.5), lower=c(0), algorithm="port")

fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.5, Vr_o=0.3), lower=c(0,0), algorithm="port")

@@

model1_val <- as.data.frame(confint2(fit_children)) %>%
  mutate(val= Vr_ch, 
         model=1, 
         group = "children") %>%
  bind_rows(as.data.frame(confint2(fit_adults)) %>%
              mutate(val= Vr_ad, 
                     model=1, 
                     group = "adults"))

model2_val <- add_rownames(as.data.frame(confint2(fit_children_2)), "param") %>%
  mutate(val= ifelse(param=='Vr_s',Vr_s_ch, Vr_o_ch),
         model=2, 
         group = "children") %>%
  bind_rows(add_rownames(as.data.frame(confint2(fit_adults_2)), "param") %>%
              mutate(val= ifelse(param=='Vr_s',Vr_s_ad, Vr_o_ad),
                     model=2, 
                     group = "adults"))

feather::write_feather(model1_val, "../saved_data/values_mod1.feather")       
feather::write_feather(model2_val, "../saved_data/values_mod2.feather")

model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))

@@

feather::write_feather(model_data, "../saved_data/data_correlations.feather")

@@

s = seq(-1,2.5,0.01)
y = Gdist(0,1,x)

illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))

illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
illustration$type <- factor(illustration$type, levels = c("Disambiguation", "Development"))

probs <- subset(subset(illustration, x==0)) %>%
  group_by(type, case) %>%
  mutate(prob = round(y/sum(y),2)) %>%
  filter(rep=='1')

ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      strip.text = element_text(size = 11),
      aspect.ratio = 0.5
      )+
  #xlim(c(-1,1))+
  #ylim(c(0,1))+
  #geom_vline(xintercept = 0.0, color="red") +
  #geom_segment(aes(x = 0, y = 0, xend = 0, yend = y, colour = rep),
  #             position=position_dodge(width = .2), 
   #            data = subset(illustration, x==0))+

  geom_col(aes(x = x, y = y, fill = rep),
               position=position_dodge(), 
               width=0.2,
               data = subset(illustration, x==0))+
  geom_text(aes(label=paste("Acc=", prob, sep="")),
            x=2, y=1, size=4, 
            fontface = "bold",
            data=probs)+
  xlab("Perceptual space") + ylab("Prob") +
  facet_grid(type~case) +
  theme(legend.position="none")
